On Devon Allen's Disqualification at the 2022 Track and Field World Championship

### 2023-04-11 Manuscript/manuscript.tex
added comments about womens data

%5
The rest of this paper is as follows: Section~\ref{sec:Data} describes how data was
collected and begins to detail the GLMM model which is further developed in the
Section~\ref{sec:Methods}.  The signed-rank test analysis for the same athletes is
also included in the Section~\ref{sec:Methods}.  The Section~\ref{sec:Results}
section provides the probabilities from the methods section and the paper ends 
by questioning the reaction time barrier.

@@

One conclusion from \citet{zhang2021correlation}'s analysis was that athletes
reaction times improved from 2011 to 2019.  However this study does not consider 
data from 1999 to 2009, and over this timespan athletes get slower and then
faster.  A boxplot~\ref{fig:Boxplot} shows that for the men's pooled data, the 
year with the fastest median reaction time before 2022 was 1999.  Thus, this 
reject's Zhang's conclusion that athletes are getting faster because they were 
fast over twenty years ago.  Instead, a more appropriate conclusion may be that
there is a lot of variability in reaction times as evidenced by the two fastest
years occurring 23 years apart.

@@

>>>>

%5
The rest of this paper is as follows: Section~\ref{sec:Data} describes how data was
collected and begins to detail the GLMM model which is further developed in the
Section~\ref{sec:Methods}.  The signed-rank test analysis for the same athletes is
also included in the Section~\ref{sec:Methods}.  The Section~\ref{sec:Results}
section provides the probabilities from the methods section and the paper ends 
by questioning the reaction time barrier.  Lastly, the section~\ref{sec:Discussion}
discusses the impact and limitations of the paper.

@@

One conclusion from \citet{zhang2021correlation}'s analysis was that athletes
reaction times improved from 2011 to 2019.  However this study does not consider 
data from 1999 to 2009, and over this timespan athletes get slower and then
faster.  A boxplot~\ref{fig:Boxplot} shows that for the men's pooled data, the 
year with the fastest median reaction time before 2022 was 1999.  Thus, this 
reject's Zhang's conclusion that athletes are getting faster because they were 
fast over twenty years ago. One possible explanation for why 2011 had such
high variation was because of the IAAF rule discussed earlier that increased the
penalty of a false start to an instant disqualification \citep{False-Start}.
Athletes may have been overly cautious to false start and may have consciously
or sub-consciously reacted slower as a result.  Instead, a more appropriate 
conclusion may be that there is a lot of variability in reaction times and that
the context behind the races matters.

@@

This paper does not consider data from the women's 100 meter hurdle, and although
that was initially because of concerns over reaction time differences in men and
women, exploratory analysis was performed and showed that 2022 was at best only
slightly faster relative to other championships going back to 2022.  Likewise,
the rank based comparisons results in p values that were not significant.  The
lack of evidence from looking at the women's data makes it harder to conclude 
that the sensors used at the 2022 championships were faulty, although it is
unknown if the sensors for the men's 110 meter hurdle and women's 100 meter
hurdle were the same.
